Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
Better bound on OPT

  Now we lower bound the cost of $\OPT$ by $\OPT(\sigma_I) +\OPT(\sigma_E)+\OPT(M)$, with $\sigma_I$ and $\sigma_E$ defined with respect to components of \TAlg, and $\OPT(M)$ denoting the cost of migrations performed by $\OPT$.
  %We split the cost of $\OPT$ into parts coming from serving $\sigma_I$ and $\sigma_E$.
  While serving these requests, $\OPT$ may perform migrations, and we account for them in both parts.

@@

  We have $OPT(M) + OPT(\sigma_I) \geq \alpha$, as the components of \TAlg{} could not be partitioned without splitting them, and there exist a pair of nodes with at least $\alpha$ requests between them.
  $\OPT$ either served them remotely or performed a migration.

  Now we bound $\OPT(M) + \OPT(\sigma_E))$.

>>>>

  Now we lower bound the cost of $\OPT$ in this phase.
  We define $\OPT(\sigma_I)$ and $\OPT(\sigma_E)$, with $\sigma_I$ and $\sigma_E$ defined with respect to components of \TAlg.
  By $\OPT(M)$ we denote the cost of migrations performed by $\OPT$.

  We split the cost of $\OPT$ into parts coming from serving $\sigma_I$ and $\sigma_E$.
  While serving these requests, $\OPT$ may perform migrations, and we account for them in both parts.
  We have $\OPT \geq (\OPT(\sigma_I) + \OPT(M)) + (\OPT(\sigma_E) + \OPT(M))$.

@@

  %First, we estimate the cost related to $\sigma_I$.
  We have $OPT(M) + OPT(\sigma_I) \geq \alpha$, as the components of \TAlg{} could not be partitioned without splitting them, and there exist a pair of nodes with at least $\alpha$ requests between them.
  $\OPT$ either served them remotely or performed a migration.
  We obtain $\OPT \geq \max\{\alpha, \OPT(\sigma_E) + \OPT(M)}$.

  Before we bound the competitive ratio, we relate the costs of $\TAlg$ and $\OPT$ related to $\sigma_E$.

  Second, we estimate the cost related to $\sigma_E$.
  Now we bound the cost that $\OPT$ incurred while serving requests $\sigma_E$.
  If $\OPT$ would

  Now we bound the competitive ratio.
